Introduction to latent means models in R

### 2024-02-19 README.qmd
Update readme

Repository for materials supporting our manuscript discussing practical implementations of latent mean centering in multilevel models of longitudinal psychological data.

- Repo on GitHub: <https://github.com/mvuorre/latent-mean-centering-ms>
- Archived repo: tbd
- Online: tbd

@@

Once the computations are finished the rendered documents are in docs/.

>>>>

Repository for our manuscript discussing an [R](https://cran.r-project.org/) and [brms](https://cran.r-project.org/web/packages/brms/) implementation of latent mean centering in multilevel models of longitudinal psychological data.

- Repo on GitHub: <https://github.com/mvuorre/latent-mean-centering-ms>
- Archived repo: tbd
- Online: tbd
- preprint: tbd

@@

Once the computations are finished (this will take a long time depending on your computer) the rendered documents are in `docs/`.
